JStudy exploratory data analysis

### 2021-04-28 R/exploration.Rmd
add timeseries graph by retrieval block

### Museum task retrieval

@@

```{r}
retrieval <- r_facts %>%
  select(subj_num, group, group_trial_num, retrieval_block, retrieval_trial_num, category, acc_recall, rt_recall = rt) %>% 
  left_join(r_pics %>%
              mutate(resp = resp - 50,
                     acc = if_else(is_old == resp_binary, abs(resp), -abs(resp))) %>%
              select(subj_num, group, group_trial_num, category, pic_is_old = is_old, acc_pic = acc, rt_pic = rt)) %>% 
  left_join(r_source %>%
              mutate(resp = resp - 50,
                     acc = if_else(encoding_block == resp_binary, abs(resp), -abs(resp))) %>%
              select(subj_num, group, group_trial_num, category, acc_source = acc, rt_source = rt)) %>%
  left_join(encoding %>% 
              select(subj_num, group, group_trial_num, category, interest = resp)) %>% 
  mutate(retrieval_block = case_when(retrieval_block <= 4 ~ "ep_same_sem_same",
                                     retrieval_block <= 8 ~ "ep_same_sem_diff",
                                     retrieval_block <= 12 ~ "ep_diff_sem_same",
                                     retrieval_block <= 16 ~ "ep_diff_sem_diff",
                                     TRUE ~ NA_character_))
```

>>>>

## Museum task retrieval

@@

```{r}
retrieval <- r_facts %>%
  select(subj_num, group, group_trial_num, retrieval_block, ep_is_same, sem_is_same, retrieval_trial_num, category, acc_recall, rt_recall = rt) %>% 
  left_join(r_pics %>%
              mutate(resp = resp - 50,
                     acc = if_else(is_old == resp_binary, abs(resp), -abs(resp))) %>%
              select(subj_num, group, group_trial_num, category, pic_is_old = is_old, acc_pic = acc, rt_pic = rt)) %>% 
  left_join(r_source %>%
              mutate(resp = resp - 50,
                     acc = if_else(encoding_block == resp_binary, abs(resp), -abs(resp))) %>%
              select(subj_num, group, group_trial_num, category, acc_source = acc, rt_source = rt)) %>%
  left_join(encoding %>% 
              select(subj_num, group, group_trial_num, category, interest = resp)) %>% 
  mutate(retrieval_block_type = case_when(retrieval_block <= 4 ~ "ep_same_sem_same",
                                          retrieval_block <= 8 ~ "ep_same_sem_diff",
                                          retrieval_block <= 12 ~ "ep_diff_sem_same",
                                          retrieval_block <= 16 ~ "ep_diff_sem_diff",
                                          TRUE ~ NA_character_))
```

```{r}
retrieval %>% 
  ggplot(aes(x = retrieval_trial_num, y = acc_recall)) +
  geom_rect(aes(x = NULL, y = NULL, xmin = xmin, xmax = xmax, fill = interaction(ep_is_same, sem_is_same)),
            data = retrieval %>%
              select(subj_num, retrieval_block, retrieval_trial_num, ep_is_same, sem_is_same) %>%
              group_by(subj_num, retrieval_block) %>%
              filter(retrieval_trial_num %in% range(retrieval_trial_num)) %>%
              mutate(xtype = if_else(retrieval_trial_num == min(retrieval_trial_num), "xmin", "xmax")) %>%
              ungroup() %>%
              pivot_wider(names_from = xtype, values_from = retrieval_trial_num) %>% 
              mutate(xmin = xmin - 0.5,
                     xmax = xmax + 0.5),
            ymin = 0, ymax = 1, alpha = 0.5) +
  geom_line() +
  geom_point(aes(color = retrieval_block)) +
  scale_colour_viridis_b() +
  facet_grid(subj_num ~ .)
```

```{r}
retrieval %>% 
  group_by(subj_num, ep_is_same, sem_is_same) %>% 
  summarize(mean_acc = mean(acc_recall))
```
